Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 algorithm_regret.tex
accepted Peter's changes

We next bound the regret incurred in time steps with large regret.
Let the random variable $t_s$ be the final time step in phase $s$,
for each $s$.
\dkcomment{We have already used $t_s$ before, e.g., in the preceding
  formula. Do we need to redefine it here?}
Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
time step in the \Kth{s} phase,
with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
i.e., $k > t_{s}-t_{s-1}$.
By Lemma~\ref{lem:right-choice},
under \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}}, no agent at time $t$ will incur
regret more than $g(s)$.
\dkcomment{Instead of the extra case distinction, I had thought of
  defining $g(s)$ to be the minimum of the current definition and
  \TieCutoff. Unfortunately, I think that we cannot necessarily apply
  Lemma~\ref{lem:right-choice} with that definition. Just putting that
  here in case you are thinking of simplifying the proof this way.}

>>>>

We next bound the regret incurred in time steps with large regret.
Let the random variable $t_s$ be the final time step in phase $s$,
for each $s$.
\dkcomment{We have already used $t_s$ before, e.g., in the preceding
  formula. Do we need to redefine it here?}
\pfcomment{Above we define $t_s$ to be the start time of phase $s$.}
\dkcomment{So the new $t_s$ is the old $t_{s+1}-1$? That's a really
  confusing subtle notation change. Is there a way we can avoid this
  and just decide on one or the other, and use it consistently?}
Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
time step in the \Kth{s} phase,
with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
i.e., $k > t_{s}-t_{s-1}$.
By Lemma~\ref{lem:right-choice},
under \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}}, no agent at time $t$ will incur
regret more than $g(s)$.
\dkcomment{Instead of the extra case distinction, I had thought of
  defining $g(s)$ to be the minimum of the current definition and
  \TieCutoff. Unfortunately, I think that we cannot necessarily apply
  Lemma~\ref{lem:right-choice} with that definition. Just putting that
  here in case you are thinking of simplifying the proof this way.}
